Cover letter - Bibat, Batteries-included Bayesian analysis template

### 2024-01-25 paper/jmlr_cover_letter.qmd
small cover letter changes

XXX VERSION XXX

@@

Bibat has XXX GitHub stars and XXX active devlopers. In addition, bibat is a
PyOpenSci affiliated package: the PyOpenSci community provides rigorous peer
review (though not publication), publicity, community engagement and help with
software maintenance.

@@

The following people have already reviewed bibat for PyOpenSci and therefore
might find it easy to provide another review:

@@

Editor: @mjhajharia
Reviewer 1: @OriolAbril
Reviewer 2: @alizma

>>>>

0.2.0

@@

Bibat has 16 GitHub stars and has been actively developed over about three
years. In addition, bibat is a PyOpenSci affiliated package: the PyOpenSci
community provides rigorous peer review (though not publication), publicity,
community engagement and help with software maintenance.

@@

These people previously reviewed bibat for PyOpenSci and therefore might find it
easy to provide another review:

@@
